2nd_draft

### 2020-03-17 src/2nd_draft.Rmd
Fit 2020

1. data processing
```{r, warning=F, message=F}
## Aggregated Data
assessment_aggregate <- read.csv(here("data","assessment_aggregate.csv"))[,-1]
```

@@

>>>>

1. data processing
```{r, warning=F, message=F}
## Aggregated Data
assessment_aggregate <- read.csv(here("data","assessment_aggregate.csv"))[,-1]
assessment_2020 <- read.csv(here("data","assessment_2020.csv"))[,-1]
assessment_2020.full <- read_excel(here("data/Assessment", "2020 Only.xlsx"))
```

@@

```{r fit}
## choose full model
linear_1<-lm(rate~factor(AddressAssessorMunicipalityDesc)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount,data=assessment_aggregate)

## Fit and get PMSE
assessment_2020.agg <- assessment_2020%>%
  mutate(predict_rate = predict(linear_1,newdata = .))
resid<-assessment_2020.agg$predict_rate - assessment_2020.agg$rate
sqrt(sum(resid^2)/nrow(assessment_2020.agg))

## Final result
municipality.list = c(
  "Burnaby", 
  "Coquitlam", 
  "Delta", 
  "Langley - City", 
  "Langley - Township",
  "Maple Ridge",
  "Maple Ridge Rural", 
  "North Vancouver - City",
  "North Vancouver - Dist",
  "Pitt Meadows", 
  "Port Coquitlam", 
  "Port Moody", 
  "Richmond", 
  "Surrey", 
  "Vancouver", 
  "White Rock", 
  "West Vancouver", 
  "Bowen Island", 
  "Anmore", 
  "Belcarra",
  "Lions Bay",
  "New Westminster")

## Raw Data
a <- assessment_2020.full%>%
  filter(TaxClassCode %in% c("01","05","06"),
         AddressAssessorMunicipalityDesc %in% municipality.list)

## Aggregate Data
b <- assessment_2020.agg%>%
  select(-c(Year, assessTotal : rate))%>%
  mutate(TaxClassCode = as.factor(paste0("0",TaxClassCode)))

assessment_2020.final<- merge(a, b, by =c("AddressAssessorMunicipalityDesc", "TaxClassCode"), all.x = TRUE)

write.csv(assessment_2020.final, "../Data/Assessment/assessment_2020.final")
write.csv(b, "../Data/assessment_2020.csv")
```
